A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-03 ionic_liquids.tex
high conc review

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
\label{fig:atoms_id}
\end{figure}

@@

\subfloat[]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}
\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
Fig. (c) corresponds to the SDFs of the anions, only.}
\label{fig:sdf_ions}
\end{figure}

@@

In Fig. we present the results of each iteration according to the scheme proposed in Sec. \ref{sec:partial_pressure}. The predicted values of pressure ($P_s$) reproduce what is observed experimentaly, in the sense that $P_s$ for the system \ce{CO_2}-\ce{[emim][B(CN)_4]} is considerably smaller than the value obtained for \ce{CO_2}-[emim][Tf\textsubscript{2}N].

\begin{figure}[ht]
\includegraphics[width=\linewidth]{pressure_est.pdf}
\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles corresponding to the insertion of a \ce{CO_2} molecule in \ce{[emim][B(CN)_4]}, which was modeled according to the force fields of (circles) Koller \textit{et al.} \cite{Koller_2012}, (squares) Batista \textit{et al.} \cite{Batista_2015}, (up triangles) Liu \textit{et al.} \cite{Liu_2014}, and (x) Weber y Kirchner \cite{Weber_2016}.}
\label{fig:pressure}
\end{figure}

@@

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{atoms_id.pdf}
\caption{Adopted nomenclature for 1-ethyl-3-methylimidazolium  (\ce{[emim]^+}), tetracyano borate (\ce{[B(CN)_4]^-}) and bis(trifluoromethylsulfonyl)amide (\ce{[NTf_2]^-}).}
\label{fig:atoms_id}
\end{figure}

@@

\subfloat[]{%
  \includegraphics[width=\linewidth]{ludwigall.pdf}%
}

\subfloat[]{%
  \includegraphics[width=\linewidth]{anionanion.pdf}%
}
\caption{Spatial distribution functions (SDFs) of (a) \ce{[B(CN)_4]^-} (green) and \ce{[emim]^+} (yellow) at the isosurface values of 0.138 and 0.12, respectively; and of (b) \ce{[NTf_2]^-} (blue) and \ce{[emim]^+} (white) at the isosurface values of 0.086 and 0.063, respectively.
Fig. (c) corresponds to the SDFs of the anions plotted together.}
\label{fig:sdf_ions}
\end{figure}

@@

In Fig.~\ref{fig:pressure} we present for each system our predictions of the gas-phase pressure ($P_s$), as described in Sec.~\ref{sec:partial_pressure}.
The dotted lines are the experimental pressures, which correspond to the specified values ($P$) in the liquid-phase simulation.
Note that our results reproduce what is experimentally observed, in the sense that the calculated $P_s$ is considerably smaller for \ce{CO_2}-\ce{[emim][B(CN)_4]}.
In addition, we see that for  this system the correction to the ideal gas assumption is almost negligible, as $P_s$ is very close to the fugacity ($f^g_s$).

\begin{figure}[ht]
\includegraphics[width=\linewidth]{pressure_est.pdf}
\caption{ \ce{CO_2} \ce{[emim][B(CN)_4]} Koller \textit{et al.} \cite{Koller_2012}, (squares)}
\label{fig:pressure}
\end{figure}

@@

On of the goals of this study was to compare available force fields for \ce{[emim][B(CN)_4]}.
The model that best reproduces the experimental density is the one developed by Koller.
This is the only model that reparametrizes the LJ parameters for the boron atom.
We demonstrate that it is possible to employ rigid bodies and the DSF method for the simulation. 
computationally more efficient.
Using the expanded ensemble method, we reproduced the solvation free energy.
Koller best reproduces the experimental henry constants. 
This model was evaluated also to predict inifinite-dilution activity coefficient.
This property also depends in the solvation free energy of the pure solutes.
The results at infinite-dilution suggest a more favorable solvation. and high concentrations 
The pictures changes
